Formalizing Stack Safety as a Security Property

### 2021-10-02 submission4/main.tex
add reference to Fig 2b

10 f:   add $1,%sp      ;allocate frame
11      mov -4(%sp),-1(%sp) ;violation 1!
12      mov $0,-4(%sp)      ;violation 2!
13      mov $5,%ra      ;set return value
14      sub $1,%sp      ;deallocate frame
15      ret
    \end{lstlisting}
}
\end{subfigure}
\begin{subfigure}[]{.43\textwidth}
\centering
\addtolength{\tabcolsep}{-1em}
\begin{tabular}{l | l}
  \multicolumn{2}{c}{
    2 \hspace{-1.5em}
    \memoryaddrs{8em}
    \memory{3}{\unsealc}
    ~$\cdots$
    \vspace{.5em}
  } \\
  11 \hspace{-1.5em}
  \memoryaddrs{17em}
  \memory{1}{\unsealc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-16em}{0.75em}{42}
  &
  \memoryaddrs{17em}
  \memory{1}{\unsealc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-16em}{0.75em}{\(v_0\)}
  \MemoryLabel{-6em}{0.75em}{\(v_1\)}
  \\
  12 \hspace{-1.5em}
  \memoryaddrs{17em}
  \memory{1}{\unsealc}
  \memory{1}{\retptrc}
  \memory{1}{\badc}
  ~$\cdots$
  \MemoryLabel{-16em}{0.75em}{42}
  \MemoryLabel{-6em}{0.75em}{42}
  \vspace{.5em}
  &
  \memoryaddrs{17em}
  \memory{1}{\unsealc}
  \memory{1}{\retptrc}
  \memory{1}{\badc}
  ~$\cdots$
  \MemoryLabel{-16em}{0.75em}{\(v_0\)}
  \MemoryLabel{-6em}{0.75em}{\(v_0\)}
  \vspace{.5em}
\end{tabular}
\addtolength{\tabcolsep}{1em}
\end{subfigure}
\caption{Integrity and confidentiality violations with confidentiality traces
\ifaftersubmission\bcp{I wonder if we
    could make the figures easier to read by putting very light, differently
    colored backgrounds under the different parts} \sna{I like the minimalism of this, but the code is now set up to support playing with it}\fi}
\vspace*{-1em}
\label{fig:conf1}
\end{figure*}

\addtolength{\abovecaptionskip}{-1em}

\begin{figure}
\begin{subfigure}{.4\columnwidth}
  {\small
\begin{lstlisting}
int main() {
  int x;
  x = f();
  return g();
}

int f() {
  int y = 5;
  return y;
}

int g() {
  int z;
  return z;
}
\end{lstlisting}
  }
\vspace*{-1em}
\caption{Leaking via uninitialized data}
\vspace*{-1em}
\label{fig:conf2}
\end{subfigure}
\begin{subfigure}{.5\columnwidth}
  \begin{center}
\begin{tabular}{l l}
2 &
\memoryaddrs{8em}
\memory{3}{\unsealc}[\unsealdesc]

~$\cdots$
\vspace{.5em}
\\
3 &
\memoryaddrs{8em}
\memory{3}{\unsealc}
~$\cdots$
    \MemoryLabel{-15em}{0.75em}{42}
    \vspace{.5em}
\\
12 &
\memoryaddrs{16em}
\memory{1}{\mainsealc}[\sealdesc{0}]%
\memory{1}{\retptrc}[\retptrdesc]%
\memory{1}{\unsealc}[\unsealdesc]
~$\cdots$
\MemoryLabel{-16em}{0.75em}{42}
\MemoryLabel{-7.5em}{0.75em}{42}
\vspace{.5em}
\\
13 &
\memoryaddrs{16em}
\memory{1}{\mainsealc}
\memory{1}{\retptrc}
\memory{1}{\unsealc}
~$\cdots$
\MemoryLabel{-15em}{0.75em}{\bf 0}
\vspace{.5em}
\end{tabular}
\end{center}
\caption{Integrity Trace}
\label{fig:int1}
\end{subfigure}
\caption{}
\end{figure}

@@

Returning to the code in Figure~\ref{fig:conf1}, line 12 violates integrity.
In the initial memory layout the entire stack is {\em unsealed},
meaning that it is eligible to be written to. At the call from {\tt main} to
{\tt f}, {\tt main}'s locals are {\em sealed} with {\tt main}'s depth,
in this case 0. (Note that this does not include the return address, which is saved
by the call instruction.)
Sealing is the fundamental integrity contract between the caller and callee:
{\tt main} expects that {\tt f} will not change {\tt x}.
This leads to a simple, intuitive statement of {\em stepwise integrity}:
if a element is sealed before a step, it will be unchanged afterward.
Overwriting {\tt x} violates this property.

>>>>

10 f:   add $1,%sp      ;allocate frame
11      mov -4(%sp),-1(%sp) ;violation 1!
12      mov $0,-4(%sp)      ;violation 2!
13      mov $5,%ra      ;set return value
14      sub $1,%sp      ;deallocate frame
15      ret
    \end{lstlisting}
}
\end{subfigure}
\begin{subfigure}[]{.43\textwidth}
\centering
\addtolength{\tabcolsep}{-1em}
\begin{tabular}{l | l}
  \multicolumn{2}{c}{
    2 \hspace{-1.5em}
    \memoryaddrs{8em}
    \memory{3}{\unsealc}
    ~$\cdots$
    \vspace{.5em}
  } \\
  11 \hspace{-1.5em}
  \memoryaddrs{17em}
  \memory{1}{\unsealc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-16em}{0.75em}{42}
  &
  \memoryaddrs{17em}
  \memory{1}{\unsealc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-16em}{0.75em}{\(v_0\)}
  \MemoryLabel{-6em}{0.75em}{\(v_1\)}
  \\
  12 \hspace{-1.5em}
  \memoryaddrs{17em}
  \memory{1}{\unsealc}
  \memory{1}{\retptrc}
  \memory{1}{\badc}
  ~$\cdots$
  \MemoryLabel{-16em}{0.75em}{42}
  \MemoryLabel{-6em}{0.75em}{42}
  \vspace{.5em}
  &
  \memoryaddrs{17em}
  \memory{1}{\unsealc}
  \memory{1}{\retptrc}
  \memory{1}{\badc}
  ~$\cdots$
  \MemoryLabel{-16em}{0.75em}{\(v_0\)}
  \MemoryLabel{-6em}{0.75em}{\(v_0\)}
  \vspace{.5em}
\end{tabular}
\addtolength{\tabcolsep}{1em}
\end{subfigure}
\caption{Integrity and confidentiality violations with confidentiality violation traces
\ifaftersubmission\bcp{I wonder if we
    could make the figures easier to read by putting very light, differently
    colored backgrounds under the different parts} \sna{I like the minimalism of this, but the code is now set up to support playing with it}\fi}
\vspace*{-1em}
\label{fig:conf1}
\end{figure*}

%\addtolength{\abovecaptionskip}{-1em}

\begin{figure}
\begin{subfigure}{.4\columnwidth}
  {\small
\begin{lstlisting}
int main() {
  int x;
  x = f();
  return g();
}
int f() {
  int y = 5;
  return y;
}
int g() {
  int z;
  return z;
}
\end{lstlisting}
  }
\vspace*{-1em}
\caption{Leaking via uninitialized data}
\vspace*{-1em}
\label{fig:conf2}
\end{subfigure}
\begin{subfigure}{.5\columnwidth}
  \begin{center}
\begin{tabular}{l l}
2 &
\memoryaddrs{8em}
\memory{3}{\unsealc}[\unsealdesc]

~$\cdots$
\vspace{.5em}
\\
3 &
\memoryaddrs{8em}
\memory{3}{\unsealc}
~$\cdots$
    \MemoryLabel{-15em}{0.75em}{42}
    \vspace{.5em}
\\
12 &
\memoryaddrs{16em}
\memory{1}{\mainsealc}[\sealdesc{0}]%
\memory{1}{\retptrc}[\retptrdesc]%
\memory{1}{\unsealc}[\unsealdesc]
~$\cdots$
\MemoryLabel{-16em}{0.75em}{42}
\MemoryLabel{-7.5em}{0.75em}{42}
\vspace{.5em}
\\
13 &
\memoryaddrs{16em}
\memory{1}{\mainsealc}
\memory{1}{\retptrc}
\memory{1}{\unsealc}
~$\cdots$
\MemoryLabel{-15em}{0.75em}{\bf 0}
\vspace{.5em}
\end{tabular}
\end{center}
\caption{Integrity Violation Trace}
\label{fig:int1}
\end{subfigure}
\caption{}
\end{figure}

@@

Returning to the code in Figure~\ref{fig:conf1}, line 12 violates integrity.
In the initial memory layout the entire stack is {\em unsealed},
meaning that it is eligible to be written to. At the call from {\tt main} to
{\tt f}, {\tt main}'s locals are {\em sealed} with {\tt main}'s depth,
in this case 0. (Note that this does not include the return address, which is saved
by the call instruction.)
Sealing is the fundamental integrity contract between the caller and callee:
{\tt main} expects that {\tt f} will not change {\tt x}.
This leads to a simple, intuitive statement of {\em stepwise integrity}:
if a element is sealed before a step, it will be unchanged afterward.
Overwriting {\tt x} violates this property, as shown in Figure~\ref{fig:int1}.
